\chapter{Introduction}\label{introduction}

Mobile indoor robots have become a common sight. Over 15 million units
of iRobot's Roomba vacuum robots have been sold since their introduction
in 2002 \footnote{http://www.irobot.com/About-iRobot/Company-Information/History.aspx}.
Applications are not limited to vacuuming: There are service robots,
entertainment robots, mapping robots, security robots, and many others.
Mobile indoor robots in commercial spaces are upheld as ``the next big
thing''\footnote{http://spectrum.ieee.org/automaton/robotics/robotics-hardware/indoor-robots-for-commercial-spaces}.

Robotic navigation has also come a long way. The first vacuum robots
were merely equipped with a bumper sensor that let them to traverse a
room like a TV's DVD logo animation screensaver. In 2010, Neato Robotics
managed to develop and integrate a low-cost Lidar
\footnote{https://www.sparkfun.com/news/490} that first enabled path
planning for their vacuum robot. Some robots like LG's
Hom-bot\footnote{https://www.youtube.com/watch?v=UANWyiDf3hA} later used
ceiling cameras with visual slam (simultaneous localization and mapping)
for optical odometry information, but it was not before 2014 that iRobot
brought a vacuum robot to the market that used visual slam to create a
map of its environment \footnote{https://www.technologyreview.com/s/541326/the-roomba-now-sees-and-maps-a-home/}.

There are still stories about vacuum robots failing hilariously in their
navigation capabilities, including one woman's hair being eaten as she
slept\footnote{https://www.theguardian.com/world/2015/feb/09/south-korean-womans-hair-eaten-by-robot-vacuum-cleaner-as-she-slept},
and of course countless examples of the joke ``What is worse than
finding dog poop on the carpet? Your robot vacuum finding dog poop on
the carpet''\footnote{http://www.boredpanda.com/robot-vacuum-cleaner-spreads-dog-shit-everywhere/}.
Other obstacles that are really difficult to see with the sensors of
today's vacuum robots are very thin objects (like thin chair legs) in
the case of visual navigation, and transparent surfaces like windows and
glass walls with both visual and laser sensors. While theoretically it
would be possible to detect mirrors just the way humans do it, by
observing the geometry visible during movement and inferring the mirrors
position and orientation, no home robot has demonstrated that capability
so far.

Of course, the home robot owners want their robot to have better
navigational skills. A robot is more efficient if it can plan a path
with knowledge of all obstacles on it. That translates to quicker
cleaning. On the other hand it is safer, because the robot won't break
things and won't get hurt if it does not bump into potentially dangerous
things.

Thanks to recent efforts in miniaturization and falling costs, there is
a new option in the search for better navigation and obstacle sensors.
Usually associated with ship and aircraft localization, radar technology
made its way to the automotive industry in the form of weather-proof
range sensors. The newest sensors are even quite small (some sensors
come with antennas integrated in silicon) and cheap, with prices
projected to fall below 1€ \cite{Brouwer2015}. Today's embedded
processors are also powerful enough to handle any kind of radar signal
processing. Combined with the easy licensing in the Industrial,
Scientific, Medical (ISM) frequency bands, it seems very worthwhile to
investigate how the use of radar will improve obstacle sensing in mobile
home robots.

There have been successful attempts at using scanning radars to create better maps of a robot's environment. In consumer products like vacuum cleaning robots, mechanical parts like a spinning radar turret pose a design challenge: Can a moving mechanical part be designed to be maintenance-free, precise and still come at a cost low enough to reach an overall price that is attractive for the prospective customer? This thesis contributes a novel radar mapping method that pushes a new corner in the design space of such systems. Reprojection mapping is based only on the ratio between a target's radial speed and the sensor's speed of motion, which makes mapping with scanless range sensors possible. Real-world experiments show that in a static environment previously very challenging obstacles like chair legs and glass walls can now be mapped.

To understand why, and how radar should be integrated in next-generation home robots the next \cref{theoretical-background} will give a brief overview of conventional sensing techniques as well as the theoretical background of radar sensing, which lays the foundation of why radar reprojection can work. In section \cref{novel-approach-reprojection-mapping}, reprojection mapping, the novel technique for mapping with unsteered range sensors, is proposed. \Cref{implementation} then details a proof-of-concept implementation of the method. Results of experiments with this method are listed in \cref{results-and-evaluation} and discussed and compared in \cref{discussion-and-comparison}. \Cref{conclusion} finally concludes the thesis with an outlook and a final word on how reprojection mapping fits into the bigger picture of obstacle sensing.